Maximum Entropy Spectral Analysis: a case study

### 2021-03-03 paper/mesa.tex
Changed peaks figure

\begin{figure}
    \centering
     \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates.pdf}
      \caption{Average spectrum for the three different loss function as compared with the ``true" PSD. The average is computed with $500$ realization of a $40960$ points long time series.}
       \label{fig:ligospectrum}
\end{figure}
In figure \ref{fig:ligospectrum}, we report the original spectrum and the ensemble averaged spectrum obtained with the three methods (no confidence level).
In figure \ref{fig:ligo1peak} and \ref{fig:ligo2peak}, we plot a details od fig.~\ref{fig:ligospectrum} around the two peaks of the spectrum
In figure~\ref{fig:LigoOrderError}, we report, as above, a scatter plot with the frequency averaged error (eq.~\ref{eq:freq_error}) and the length of the autoregressive model obtained with each loss function.

The conclusions are very similar to those above. When averaged on multiple realization, CAT loss function is able to capture the spectrum very precisely.
In fact, even in presence of very sharp peaks, CAT reconstruction seems to be almost perfectly coincident with each of them (figs.\ref{fig:ligo1peak} and \ref{fig:ligo2peak}).
However, the computation on a single noise realization yields larger error, as manifest in fig.~\ref{fig:LigoOrderError}.
This supports the conclusion that CAT is not a stable optimizer: different computation of the same spectrum can output very different results.
On the other hand, FPE seems more robust and provides a smaller variance (and frequency averaged error), despite having a worse performance on the average.
We find again that FPE and OBD have similar performance: indeed, OBD shows qualitatively the same behaviour of FPE, although with slightly worse performance in the error.

@@

\begin{figure}[t]
        \includegraphics[width = \linewidth]{Images/LIGOsimulate/1stPeakComparison.pdf}
        \caption{1st peak of the spectrum and it reconstruction with every optimizer (left) and associated percentage error (right) \sschmidt{This should be done with the same style as the others}}
        \label{fig:ligo1peak}
\end{figure}
\begin{figure}[t]
    \centering
        \includegraphics[width = \linewidth]{Images/LIGOsimulate/2ndPeakComparison.pdf}
        \caption{2nd peak of the spectrum, Relative error around 2nd peak of the spectrum \sschmidt{This should be done with the same style as the others}}
        \label{fig:ligo2peak}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/error_length_contour.pdf}
    \caption{For each of the $500$ independent realization of the time series, we plot the relative error $r$ (as in eq.~\ref{eq:freq_error}) against the length $m$ of autoregressive process. The time series are randomly drawn with a the analytical LIGO PSD in fig.`\ref{fig:ligospectrum}. Different colors refers to different choices for the loss function. Histograms for the distribution od the individual quantities are also represented.}
    \label{fig:LigoOrderError}
\end{figure}

>>>>

\begin{figure}
    \centering
     \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates.pdf}
      \caption{Average spectrum for the three different loss function as compared with the ``true" PSD. The average is computed with $500$ realization of a $40960$ points long time series.}
       \label{fig:ligospectrum}
\end{figure}
In figure \ref{fig:ligospectrum}, we report the original spectrum and the ensemble averaged spectrum obtained with the three methods (no confidence level).
In figure \ref{fig:ligoPeaks} we plot a details od fig.~\ref{fig:ligospectrum} around the two peaks of the spectrum
In figure~\ref{fig:LigoOrderError}, we report, as above, a scatter plot with the frequency averaged error (eq.~\ref{eq:freq_error}) and the length of the autoregressive model obtained with each loss function.

The conclusions are very similar to those above. When averaged on multiple realization, CAT loss function is able to capture the spectrum very precisely.
In fact, even in presence of very sharp peaks, CAT reconstruction seems to be almost perfectly coincident with each of them (figs.\ref{fig:ligoPeaks}).
However, the computation on a single noise realization yields larger error, as manifest in fig.~\ref{fig:LigoOrderError}.
This supports the conclusion that CAT is not a stable optimizer: different computation of the same spectrum can output very different results.
On the other hand, FPE seems more robust and provides a smaller variance (and frequency averaged error), despite having a worse performance on the average.
We find again that FPE and OBD have similar performance: indeed, OBD shows qualitatively the same behaviour of FPE, although with slightly worse performance in the error.

@@

\begin{figure}[t]
        \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates_peaks.pdf}
        \caption{Details of peaks of the spectrum and their reconstruction with every optimizer}
        \label{fig:ligoPeaks}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/error_length_contour.pdf}
    \caption{For each of the $500$ independent realization of the time series, we plot the relative error $r$ (as in eq.~\ref{eq:freq_error}) against the length $m$ of autoregressive process. The time series are randomly drawn with a the analytical LIGO PSD in fig.`\ref{fig:ligospectrum}. Different colors refers to different choices for the loss function. Histograms for the distribution od the individual quantities are also represented.}
    \label{fig:LigoOrderError}
\end{figure}
